Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-08-06 talk/dls2012/paper.tex
clarify

\reva{
First sentence of the related work section is kind of
unfortunate. It is unclear what the reference at the end of the
sentence is good for. To support the meaning of the entire sentence?
Or is it just a reference to the standard loop invariant code motion
techniques? The contribution of your paper seems much smaller than
in the former case compared to the latter one. While I have not
checked the content of the book, I believe the latter is the correct
interpretation. You should remove this opportunity for
misinterpretation.}

The effect of combining a one pass optimization with loop peeling gives
completely standard loop invariant code motion optimizations
\cite{muchnick_advanced_1997}. We do not claim any novelty in the effect, but
think that our implementation scheme is a very simple one.

>>>>

Loop invariant code motion optimizations are completely
standard~\cite{muchnick_advanced_1997}. Therefore, the effects that our
optimization achieves is not in any way new. However, we think that achieving
it as described in this paper is simpler than explicit algorithms.
